Efficient pedigree recording for fast population genetics simulation

### 2018-01-08 forwards_paper.tex
labeling bug in #45

\begin{figure}
    \begin{center}
        \includegraphics{method_diagram}
    \end{center}
    \caption{
        An example of tree sequence simplification.
        \textbf{Top:} the augmented pedigree diagram on the left 
        relates the ten homologous chromosomes of five diploid individuals (BC, DE, FG, HI, and JK) 
        to each other and to a common ancestral chromosome (A);
        dotted lines connect the two chromosomes of each individual, and solid lines lead to the products of their meioses.
        The corresponding tables (right) have 10 node records (one for each chromosome)
        and 14 edge records (one for each distinctly inherited segment).
        Blue numbers denote crossing over locations --
        for instance, $D$ and $E$ were parents to $F$,
        who inherited the left 70\% of the chromosome from $E$ and the remainder from $D$.
        $B$, $C$, $D$, and $E$ inherit clonally from $A$.
        \textbf{Center:} the five distinct trees
        found across the chromosome (blue numbers denote locations on the chromosome).
        Labels after simplification are shown in red.
        \textbf{Bottom:} tables recording the tree sequence after simplification
        with nodes $I$ and $J$ as samples.
        The mapping from labels in the forwards time simulation to nodes in the tree sequence
        is shown in red.
        % which allows additional records to be added as the simulation progresses.
        \label{fig:method_diagram}
    }
\end{figure}

>>>>

\begin{figure}
    \begin{center}
        \includegraphics{method_diagram}
    \end{center}
    \caption{
        An example of tree sequence simplification.
        \textbf{Top:} the augmented pedigree diagram on the left 
        relates the ten homologous chromosomes of five diploid individuals (BC, DE, FG, HI, and JK) 
        to each other and to a common ancestral chromosome (A);
        dotted lines connect the two chromosomes of each individual, and solid lines lead to the products of their meioses.
        The corresponding tables (right) have 10 node records (one for each chromosome)
        and 14 edge records (one for each distinctly inherited segment).
        Blue numbers denote crossing over locations --
        for instance, $D$ and $E$ were parents to $G$,
        who inherited the left 70\% of the chromosome from $E$ and the remainder from $D$.
        $B$, $C$, $D$, and $E$ inherit clonally from $A$.
        \textbf{Center:} the five distinct trees
        found across the chromosome (blue numbers denote locations on the chromosome).
        Labels after simplification are shown in red.
        \textbf{Bottom:} tables recording the tree sequence after simplification
        with nodes $J$ and $K$ as samples.
        The mapping from labels in the forwards time simulation to nodes in the tree sequence
        is shown in red.
        % which allows additional records to be added as the simulation progresses.
        \label{fig:method_diagram}
    }
\end{figure}
